Perturbation theories in the complex plane

### 2020-06-29 SlideToulouse/main.tex
Add files via upload

\begin{equation}
   F = T + J + K
\end{equation}

@@

\begin{itemize}
\centering
    \item $T$: Kinetic energy operator
    \item $J$: Coulomb operator
    \item $K$: Exchange operator
\end{itemize}

@@

\begin{beamerboxesrounded}[scheme=foncé]{}
\centering

Full Configuration Interaction gives access to high-order terms of the perturbation series!

@@

\begin{figure}
    \centering

    \includegraphics[width=0.45\textwidth]{gill1986.png}

    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
    \label{fig:my_label}
\end{figure}

@@

@@

\begin{equation*}
    H(\lambda)=\sum\limits_{j=1}^{2n}\left[ \underbrace{-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}}_{\text{Independant of }\lambda} + \overbrace{(1-\lambda)V_j^{(scf)}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{j<l}^{2n}\frac{1}{|\vb{r}_j-\vb{r}_l|}}_{\textcolor{blue}{Attractive}}  \right]
\end{equation*}

@@

\section{The spherium model}

\begin{frame}{Spherium: a theoretical playground\footcite{loos_ground_2009}}

\begin{beamerboxesrounded}[scheme=foncé]{\centering Two electrons on a sphere Hamiltonian}
\begin{equation*}
    H=-\frac{1}{2}(\grad_1^2 + \grad_2^2) + \frac{1}{r_{12}}
\end{equation*} 
\end{beamerboxesrounded}
\vspace{0.5cm}

\centering{Small $R$}
\vspace{0.5cm}

\begin{itemize}
    \item $E_\text{kin} \gg E_\text{pot}$
    \item Uniform density of electrons
    \item \textcolor{red}{Weak correlation}
\end{itemize}

\centering{Large $R$}
\vspace{0.5cm}

\begin{itemize}
    \item $E_\text{kin} \ll E_\text{pot}$
    \item Electrons on the opposite sides of the sphere
    \item \textcolor{red}{Strong correlation}
    \end{itemize}

\begin{frame}{Apparition of a class $\beta$ singularity}

\begin{beamerboxesrounded}[scheme=foncé]{\centering Expectation}
The electrons are restricted to the surface of the sphere so we should not observe singularities characteristic of ionization processes.
\end{beamerboxesrounded}

\large But for some values of R... we actually observe some $\beta$ singularities!
\centering Why?

\begin{beamerboxesrounded}[scheme=foncé]{\centering Symmetry breaking}
The $\beta$ singularities observed are connected to the symmetry breaking of the wave function.
\end{beamerboxesrounded}

@@

But there is an other secret application of exceptional points...

\begin{beamerboxesrounded}[scheme=foncé]{\centering A new way to excited states energies}
The exceptionnal points connect ground and excited states in the complex plane. Using those properties one can smoothly morph a ground state in an excited state. 
\end{beamerboxesrounded}

>>>>

\begin{equation}
   F = \sum\limits_{i=1}^{n} f(i) \hspace{0.3cm} ; \hspace{0.3cm} f(i) = h(i) + \sum\limits_{i=1}^{n/2} \left[2J_j(i) - K_j(i)\right]
\end{equation}

@@

\begin{itemize}
\centering
    \item $f(i)$: Fock operator
    \item $h(i)$: One electron Hamiltonian
    \item $J_j(i)$: Coulomb operator
    \item $K_j(i)$: Exchange operator
\end{itemize}

@@

\begin{beamerboxesrounded}[scheme=foncé]{}
\centering
Full Configuration Interaction gives access to high-order terms of the perturbation series !
\end{beamerboxesrounded}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.45\textwidth]{gill1986.png}
    \caption{\centering Barriers to homolytic fission of \ce{He2^2+} at MPn/STO-3G level ($n = 1$--$20$).}
    \label{fig:my_label}
\end{figure}

@@

\begin{frame}{The Møller-Plesset Hamiltonian}

\begin{equation}
H(\lambda)=H_0 + \lambda (H_\text{phys} - H_0)    
\end{equation}

\begin{equation}
    H_\text{phys}=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|}\right]
\end{equation}

\begin{equation}
    H_0=\sum\limits_{j=1}^{n}\left[ -\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}+V_j^{(scf)}\right]
\end{equation}

@@

\begin{equation*}
    H(\lambda)=\sum\limits_{j=1}^{n}\left[ \underbrace{-\frac{1}{2}\grad_j^2 - \sum\limits_{k=1}^{N} \frac{Z_k}{|\vb{r}_j-\vb{R}_k|}}_{\text{Independant of }\lambda} + \overbrace{(1-\lambda)V_j^{(scf)}}^{\textcolor{red}{Repulsive}}+\underbrace{\lambda\sum\limits_{j<l}^{n}\frac{1}{|\vb{r}_j-\vb{r}_l|}}_{\textcolor{blue}{Attractive}}  \right]
\end{equation*}

@@

\section{Conclusion}

@@

\begin{beamerboxesrounded}[scheme=foncé]{\centering Spherium: a theoretical playground}
We will use the spherium model (two opposite-spin electrons restricted to remain on a surface of a sphere of radius $R$) to investigate the effects of symmetry breaking on singularities.
\end{beamerboxesrounded}
